---
title: " Course Assignemt : R Markdown Presentation & Plotly (WW2 Stats)"
author: "Junaid Khan"
date: "September 16, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Worldwide Deaths in World War II

World War II (often abbreviated to WWII or WW2), also known as the Second World War, was a global war that lasted from 1939 to 1945. The vast majority of the world's countries-including all the great powers-eventually formed two opposing military alliances: the Allies and the Axis. It was the most global war in history; it directly involved more than 100 million people from over 30 countries

## WORLDWIDE CASUALTIES

- Battle Deaths :15,000,000
- Battle Wounded :25,000,000
- Civilian Deaths :45,000,000

## Total Civilian and Military Deaths

```{r cars, echo = FALSE, comment=''}
df <- data.frame( country = c('China', 'Germany', 'India', 'Philippines', 'Soviet Union', 'United Kingdom', 'United States'), count = c(20000000, 	6600000, 1500000, 500000, 24000000, 450700, 418500))

df
```

```{r , echo=F}
library(plotly)
```

## Bar Chart of Death Count

```{r chart , echo=FALSE, comment=''}
suppressWarnings(plot_ly( x = df$country, y = df$count, type = "bar"))

```

